---
title: "Time Series Analysis - Gas"
author: "Muthu Pandian G"
date: "January 28, 2020"
output:
  word_document: default
  html_document: default
---
## Set the Working Directory 
```{r}
setwd("D:/Great Lakes/Projects/Time Series Analysis")
```
## Reading Data into R
```{r cars}
library(forecast)
gas <- window(gas)

```

```{r}
class(gas)
start(gas)
end(gas)
frequency(gas)
```
## Exploratory Data Analysis (EDA)

### Summary 

```{r}

summary(gas)
```

## Plotting the Time Series
```{r}
plot(gas,main = "Australian Monthly Gas Production",xlab= "Years", ylab = "Gas Production")
```


```{r}
gas1 <- window(gas,start = c(1970,1), end = c(1994,12), frequency = 12)
plot(gas1,main = "Australian Monthly Gas Production",xlab= "Years", ylab = "Gas Production")
```

## Seasonal Plots 

```{r}
ggseasonplot(gas1,main = "Australian Monthly Gas Production",xlab= "Seasons", ylab = "Gas Production")
```

#Split data into train and test sets
```{r}
gas1.train <- window(gas1,start = c(1970,1),end = c(1993,12),frequency = 12)
gas1.test<- window(gas1,start = c(1994,1),frequency = 12)

```
# Decomposing Time Series
## Decomposing Seasonal Data
```{r}
gas_Additivecomponents <- decompose(gas1.train,"additive")

autoplot(gas_Additivecomponents)
gas_Additivecomponents$seasonal
gas_Additivecomponents$trend
gas_Additivecomponents$random
```


```{r}
### Let's try and make this multiplicative
gas_multiplicativecomponents <- decompose(gas1.train,"multiplicative")

autoplot(gas_multiplicativecomponents)
gas_multiplicativecomponents$seasonal
gas_multiplicativecomponents$trend
gas_multiplicativecomponents$random
```
Still the same pattern hence series is additive.


```{r}
ses.gas <- ses(gas1.train, alpha = 0.2, h=12)
autoplot(ses.gas)
```

```{r}
accuracy(ses.gas, gas1.test)
```

#Holt winters Model

```{r}
gas.hw <- ets(gas1.train, model = "AAA")
autoplot(forecast(gas.hw))

summary(gas.hw)


# forecast the next 12 months
gas.hw.forecast <- forecast(gas.hw, h = 12)
accuracy(gas.hw.forecast, gas1.test)
```

# Stationarity
Null Hypothesis -  unit root is present in a time series sample.
Alternate Hypothesis - series is stationary 
```{r}
library(tseries)
adf.test(gas1, alternative = "stationary")
```

# ACF and PACF plots

```{r}
acf(gas1)
acf(gas1, lag.max = 50)
pacf(gas1, lag.max = 50)
```


## Seasonally Adjusting

```{r}
decomp = stl(gas1, s.window = "periodic")
deseasonal_gas=seasadj(decomp)
plot(decomp)
```

```{r}
diff_gas = diff(gas1, differences = 1)
plot(diff_gas,main = "Differenced Series")
adf.test(diff_gas, alternative = "stationary")
```
# Acf and Pacf for dif time series
```{r}
Acf(diff_gas,lag.max = 50, main='ACF for Differenced Series')
Pacf(diff_gas,lag.max = 50, main='PACF for Differenced Series')
```

Splitting into training and test sets
```{r}
gasTstrain = window(deseasonal_gas, start=c(1970,1), end=c(1993,12),frequency = 12)
gasTStest= window(deseasonal_gas, start=c(1994,1))
```


```{r}
gasarima <- arima(gasTstrain,order = c(0,1,2))
gasarima
tsdisplay(residuals(gasarima), lag.max=50, main='Model Residuals')
```

# Fitting an Auto Arima model
```{r}
Fit1 <- auto.arima(gasTstrain, seasonal = TRUE)
Fit1
tsdisplay(residuals(Fit1), lag.max=50, main='Model Residuals')
```
Auto ARIMA also fits the same p and q parameters for the model, but has a slightly lower AIC.

#Ljung box test
H0: Residuals are independent
Ha: Residuals are not independent

```{r}
library(stats)
Box.test(gasarima$residuals)

```



# Forecasting Using an Manual- ARIMA Model

```{r}
Manual_gasarima_Forecast <- forecast(gasarima, h = 12)
accuracy(Manual_gasarima_Forecast,gasTStest)  
```  
  
# Forecasting Using an Auto-ARIMA Model
```{r}
Auto_gasarima_Forecast <- forecast(Fit1, h = 12)
accuracy(Auto_gasarima_Forecast,gasTStest)
```  

