---
title: "India Credit Risk - FRA"
author: "Muthu Pandian G"
date: "March 21, 2020"
output: word_document
---

```{r echo= FALSE}
setwd("D:/Great Lakes/Projects/Domain/FRA")
getwd()
library(xlsx)
rawdata <- read.xlsx("raw-data.xlsx",sheetIndex = 1)
validation_data <- read.xlsx("validation_data.xlsx",sheetIndex = 1)
rawdata$default <- ifelse(rawdata$Networth.Next.Year>0,0,1)
summary(as.factor(rawdata$default))
243/3298
```
##Understanding the data
### Structure of Data

```{r echo= FALSE}
str(rawdata)
#str(validation_data)
sum(is.na(rawdata))
colSums(is.na(rawdata))
summary(rawdata)
```


## Missing value Treatment 
```{r echo= FALSE}
# removing Deposits (accepted by commercial banks) column as it is full of NA

rawdata <- rawdata[,-22]
validation_data <- validation_data[,-22]
rawdata.nona <- rawdata
validation_data.nona <- validation_data

rawdata.nona$Creditors.turnover <- as.numeric(rawdata.nona$Creditors.turnover)
validation_data.nona$Creditors.turnover <- as.numeric(validation_data.nona$Creditors.turnover)
rawdata.nona$Debtors.turnover <- as.numeric(rawdata.nona$Debtors.turnover)
validation_data.nona$Debtors.turnover <- as.numeric(validation_data.nona$Debtors.turnover)
rawdata.nona$Finished.goods.turnover <- as.numeric(rawdata.nona$Finished.goods.turnover)
validation_data.nona$Finished.goods.turnover <- as.numeric(validation_data.nona$Finished.goods.turnover)
rawdata.nona$WIP.turnover <- as.numeric(rawdata.nona$WIP.turnover)
validation_data.nona$WIP.turnover <- as.numeric(validation_data.nona$WIP.turnover)
rawdata.nona$Raw.material.turnover <- as.numeric(rawdata.nona$Raw.material.turnover)
validation_data.nona$Raw.material.turnover <- as.numeric(validation_data.nona$Raw.material.turnover)
rawdata.nona$Shares.outstanding <- as.numeric(rawdata.nona$Shares.outstanding)
validation_data.nona$Shares.outstanding <- as.numeric(validation_data.nona$Shares.outstanding)
rawdata.nona$Equity.face.value <- as.numeric(rawdata.nona$Equity.face.value)
validation_data.nona$Equity.face.value <- as.numeric(validation_data.nona$Equity.face.value)
rawdata.nona$PE.on.BSE <- as.numeric(rawdata.nona$PE.on.BSE)
validation_data.nona$PE.on.BSE <- as.numeric(validation_data.nona$PE.on.BSE)
sum(is.na(rawdata.nona))

for(i in 1:ncol(rawdata.nona)){
  rawdata.nona[is.na(rawdata.nona[,i]), i] <- mean(rawdata.nona[,i], na.rm = TRUE)
}

sum(is.na(rawdata.nona))

sum(is.na(validation_data.nona))

for(i in 1:ncol(validation_data.nona)){
  validation_data.nona[is.na(validation_data.nona[,i]), i] <- mean(validation_data.nona[,i], na.rm = TRUE)
}

sum(is.na(validation_data.nona))

```
## Outlier Treatment 

For values that lie outside the 1.5 * IQR limits, we could cap it by replacing those observations outside the lower limit with the value of 25th %ile and those that lie above the upper limit, with the value of 75th %ile

```{r}
boxplot(rawdata.nona$Total.assets)

fun <- function(x){
    quantiles <- quantile( x, c(.25, .75 ) )
    x[ x < quantiles[1] ] <- quantiles[1]
    x[ x > quantiles[2] ] <- quantiles[2]
    x
}
default <- rawdata.nona$default

for (i in 2:ncol(rawdata.nona)) {
rawdata.nona[,i] <- fun( rawdata.nona[,i] )  
}

rawdata.nona$default <- default
summary(as.factor(rawdata.nona$default))
boxplot(rawdata.nona$Total.assets)
summary(rawdata.nona)


```
## EDA
# Univariate Analysis 
```{r echo=FALSE}
library(ggplot2)

ggplot(rawdata.nona,aes(x = Profit.after.tax))+ geom_histogram(fill = "#009E73",colour = "Black",binwidth = 15)+ ggtitle("Profit after Tax based on Total Income") + theme(plot.title = element_text(hjust = 0.5))+xlab("Profit after Tax based on Total Income")


ggplot(rawdata.nona,aes(x = Sales))+ geom_histogram(fill = "purple",colour = "Black",binwidth = 30)+ ggtitle("Sales") + theme(plot.title = element_text(hjust = 0.5))+xlab("Sales")


ggplot(rawdata.nona,aes(x = Total.capital))+ geom_histogram(fill = "Brown",colour = "Black",binwidth = 25)+ ggtitle("Total Capital") + theme(plot.title = element_text(hjust = 0.5))+xlab("Total Capital")

ggplot(rawdata.nona,aes(x = Current.liabilities...provisions))+ geom_histogram(fill = "Red",colour = "Black",binwidth = 15)+ ggtitle("liabilities") + theme(plot.title = element_text(hjust = 0.5))+xlab("Liabilities")

ggplot(rawdata.nona,aes(x = Borrowings))+ geom_histogram(fill = "Yellow",colour = "Black",binwidth = 25)+ ggtitle("Borrowings") + theme(plot.title = element_text(hjust = 0.5))+xlab("Borrowings")


```

# Bivariate Analysis 
```{r echo=FALSE}

ggplot(rawdata.nona,aes(as.factor(default),fill = Borrowings))+geom_bar()+ggtitle("Default vs Borrowings")+ theme(plot.title = element_text(hjust = 0.5))+ xlab("Borrowings")

plot(as.factor(rawdata.nona$default),rawdata.nona$Profit.after.tax)

```
## Removing Multicollinearity 
As a rule of thumb, a VIF value that exceeds 5 or 10 indicates a problematic amount of collinearity
```{r}
library(car)
vif.model <- glm(default~.,rawdata.nona,family = "binomial")
summary(vif.model)
rawdata.nona <- rawdata.nona[,-50]
vif.model1 <- glm(default~.,rawdata.nona,family = "binomial")
alias(vif.model)
vif(vif.model1)
names(rawdata.nona)
rawdata.nona <- rawdata.nona[,-c(48,49)]
vif.model2 <- glm(default~.,rawdata.nona,family = "binomial")
vif(vif.model2)
rawdata.nona <- rawdata.nona[,-c(5)]
vif.model3 <- glm(default~.,rawdata.nona,family = "binomial")
vif(vif.model3)
rawdata.nona <- rawdata.nona[,-c(3,26)]
vif.model3 <- glm(default~.,rawdata.nona,family = "binomial")
vif(vif.model3)
rawdata.nona <- rawdata.nona[,-c(3,5,6)]
vif.model3 <- glm(default~.,rawdata.nona,family = "binomial")
vif(vif.model3)

rawdata.nona <- rawdata.nona[,-c(4,18,20)]
vif.model3 <- glm(default~.,rawdata.nona,family = "binomial")
vif(vif.model3)

rawdata.nona <- rawdata.nona[,-c(2,4,5)]
vif.model3 <- glm(default~.,rawdata.nona,family = "binomial")
vif(vif.model3)

rawdata.nona <- rawdata.nona[,-c(4,5,12,14,15,20)]
vif.model3 <- glm(default~.,rawdata.nona,family = "binomial")
vif(vif.model3)

rawdata.nona <- rawdata.nona[,-c(6,8,18)]
vif.model3 <- glm(default~.,rawdata.nona,family = "binomial")
vif(vif.model3)

rawdata.nona <- rawdata.nona[,-c(9,10,16,18)]
vif.model3 <- glm(default~.,rawdata.nona,family = "binomial")
vif(vif.model3)

validation_data.nona1 <- validation_data.nona[,c(1,2,6,12,15,16,18,20,22,30,31,33,34,35,38,40,41,42,43,44,45,46,47,51)]
```

# Logistic Regression 
```{r echo=FALSE}
Default_model <- glm(default~.,rawdata.nona,family = "binomial")
summary(Default_model)

```

```{r echo= FALSE}
Default_model1 <- glm(default~rawdata.nona$Cash.to.average.cost.of.sales.per.day+Debt.to.equity.ratio..times.+Net.working.capital+PAT.as...of.net.worth+Cash.profit.as...of.total.income+Current.assets+Investments+Borrowings+rawdata.nona$Contingent.liabilities...Net.worth....,rawdata.nona,family = "binomial")
summary(Default_model1)
plot(as.factor(Default_model1$y),Default_model1$fitted.values)

```
# Model Prediction
```{r}

Default_prediction = ifelse(Default_model1$fitted.values>0.12,1,0)
summary(as.factor(Default_prediction))

Result <- table(as.factor(Default_model1$y),Default_prediction)
Result
# Accuracy
accuracy <- round(sum(diag(Result))/sum(Result),2)
accuracy

# Sensitivity 
sensitivity <- round(2845/(2845+453),2)
sensitivity

# Specificity
specificity <-round(190/(53+190),2)
specificity

```

```{r echo= FALSE}
validation_data.nona1$default <- validation_data$Default...1
validation_data.nona1 <- validation_data.nona1[,-2]
Validation_Prediction =predict(Default_model1,validation_data.nona1,type="response")
#Validation_Prediction =ifelse(Validation_Prediction>0.90,"Default","NonDefault")
#summary(as.factor(Predicted_Validation))
#names(rawdata.nona)
```



